### 2018-01-26 Graduate - Introduction to Analysis II/HW1/1Homework20180124.tex
add problem 6-9

\item Problem III.2.7

@@

@@

@@

>>>>

\item Problem III.2.7
$$
\cos z\cos w = \frac{1}{4}(e^{iz}+e^{-iz})(e^{iw}+e^{-iw}) = \frac{1}{4}(e^{i(z+w)}+e^{-i(z+w)}+e^{i(z-w)}+e^{i(w-z)}),
$$
$$
\sin z\sin w = -\frac{1}{4}(e^{iz}-e^{-iz})(e^{iw}-e^{-iw}) = \frac{1}{4}(-e^{i(z+w)}-e^{-i(z+w)}+e^{i(z-w)}+e^{i(w-z)})
$$
$$
\cos z\sin w = \frac{1}{4i}(e^{iz}+e^{-iz})(e^{iw}-e^{-iw}) = \frac{1}{4i}(e^{i(z+w)}-e^{i(z-w)}+e^{i(w-z)}-e^{-i(z+w)})
$$
$$
\sin z\cos w = \frac{1}{4i}(e^{iz}-e^{-iz})(e^{iw}+e^{-iw}) = \frac{1}{4i}(e^{i(z+w)}+e^{i(z-w)}-e^{i(w-z)}-e^{i(z+w)})
$$
Hence, 
$$
\cos(z+w) = \frac{1}{2}(e^{i(z+w)}+e^{-i(z+w)}) = \cos z\cos w-\sin z\sin w.
$$
$$
\sin(z+w) = \frac{1}{2i}(e^{i(z+w)}-e^{-i(z+w)}) = \cos z\sin w+\sin z\cos w.
$$

@@

\textbf{Proof.} 
$$
\begin{aligned}
|z_n-z| &= |r_ne^{i\theta_n}-re^{i\theta}| = |r_n\cos(\theta_n)-r\cos(\theta) + i(r_n\sin(\theta_n)-r\sin(\theta))| \\
&= \sqrt{(r_n\cos(\theta_n)-r\cos(\theta))^2+(r_n\sin(\theta_n)-r\sin(\theta))^2} \\
&= \sqrt{r_n^2+r^2-2r_nr\cos(\theta_n-\theta)}.
\end{aligned}
$$
If $\theta_n \nrightarrow \theta $, then there exists $\epsilon > 0$
$$
|z_n-z| \ge \sqrt{2r_nr(1-\cos(\theta_n-\theta))} > \epsilon,
$$
which contradicts with $z_n\to z $. Hence $\theta_n\to \theta $. So
$$
|z_n-z| \to |r_n-r|.
$$
Thus $r_n\to r $.

@@

$z = f(z)^n \to f(z) = z^{1/n} $, take a branch. Thus
$$
f(z) = z^{1/n} = e^{\frac{1}{n}\log z} = e^{\frac{1}{n} (\log |z| + iArg z+ i2k\pi)} = |z|^{1/n}e^{\frac{i}{n}(Argz+2k\pi)}.
$$
Pick any $k\in\mathbb{Z}$ and we can get a function satisfying the conditions.

@@

$$
\log(z_1\cdots z_n) = \log|z_1\cdots z_n|+ Arg(z_1\cdots z_n).
$$
We need to show that ($Arg$ is the principle branch.)
$$
Arg(z_1\cdots z_n) = \sum Arg(z_i).
$$
and
$$
\log|z_1\cdots z_n| = \sum\log|z_i|.
$$
The second term is trivial from logarithm of real numbers. For the first term, we use induction. Let $z_j = r_je^{i\theta_j} $, then from the condition we know $-\frac{\pi}{2} < \theta_j < \frac{\pi}{2}$ (*).

First, when $k = 2$, from the condition we know $2k\pi-\frac{\pi}{2} < \theta_1 + \theta_2 < 2k\pi+\frac{\pi}{2}$. But from (*) we know $-\pi < \theta_1 + \theta_2 <\pi $, thus $-\frac{\pi}{2} <\theta_1 + \theta_2 < \frac{\pi}{2}$. Hence $Arg(z_1z_2) = Arg(z_1)+Arg(z_2)$.

Suppose it holds when $\le n-1$. Then from induction we know $-\frac{\pi}{2} <\sum\limits_{j=1}^{n-1}\theta_j < \frac{\pi}{2}$, and using the same deduction with $k = 2$, we can know $-\frac{\pi}{2} <\sum\limits_{j=1}^{n}\theta_j < \frac{\pi}{2}$. Hence $Arg(\prod z_i) = \sum Arg(z_i)$.

If the restrictions are removed, the formula is not valid. For example, $z_1 = e^{i\pi}, z_2 = e^{i\frac{3\pi}{2}} $, then $\log(z_1z_2) = i\frac{\pi}{2}$, while $\log(z_1)+\log(z_2) = i\frac{5\pi}{2}$.
